### 2019-09-07 manuscript/manuscript.tex
incorporated GC's changes in last results section

% TODO
% - we have inconsistent notation between intro of results and figure 1 with
%   cov()

@@

Finally, we observed that in the \gc{longest study}  we 
analyzed \parencite{Barghi2019-qy}, some genome-wide temporal covariances
\gc{become} negative at future timepoints (see the first two rows in
Figure \ref{fig:figure-1} A). \gc{This shows that alleles that were on
average going up initially are no going down in frequency, i.e. that
the average direction of selection experienced by alleles has
flipped. This must reflect either a change in the environment or the
genetic background, due to changing epistatic relationships among
alleles or  recombination breaking up selective alleles.}
\gc{Such reversals of selective dynamics could be occuring at other time-points but} the
signal of a change in the direction of selection \gc{at particular
  loci} may be washed out when we calculate our  genome-wide \gc{average} temporal
covariances. To address this limitation, we
calculated \gc{the distribution of the} temporal covariances over
100kb genomic windows \gc{(Figure \ref{fig:figure-3}, pooling
across all replicates see Supplementary Figure \ref{suppfig:barghi-offset-replicate-panels} for individuals replicates).}
\gc{The}
covariance of each tile \gc{will be} noisy, \gc{due to sampling and genetic
  drift, and the neutral distribution of the covariance is
  complicated due to} linkage
disequilibria (which can occur over long physical distances in E\&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}). 
\gc{Thus} we have developed a permutation-based procedure that constructs a null
distribution by randomly flipping the signs of the    %of the
                                %genome-wide covariances as they would
                                %look if only neutral genetic drift was acting. We do this 
allele frequency changes per-genomic window. \gc{This destroys}  %%  GC bit about 1,000 times seems more like figgure caption or methods
the systematic covariances created by linked selection but creates a sampling
distribution of the covariances spuriously created by neutral genetic
drift while preserve the complex dependencies
between adjacent loci created by linkage disequilibrium (see Supplementary
Material Section \ref{supp:empirical-null} for more details on this approach).
This empirical neutral null distribution is conservative in the sense that the
variances of the covariances are wider than expected under drift
alone \gc{as they include the effect of selection on the allele
  frequency change within a time-interval, just not between
  time-intervals.} We see, Figure \ref{fig:figure-3} A and B, that
windowed temporal covariances between close timepoints are skewed positive (a
heavy right tail), while between more distant timepoints these windowed
temporal covariances tend to shift to become more negative (a heavy
left tail).
We quantified the degree to which the left and right
tails \gc{are inflated compared to the null distribution as a function
  of time}, and see excesses in both tails in Figure
\ref{fig:figure-3} C. This finding is also
robust to sign-permuting allele frequency changes on a chromosome-level, the
longest extent that gametic linkage disequilibria can extend {\bf ????} (Supplementary
Figure \ref{suppfig:barghi-tailprobs-seqid}).  \gc{We} see a striking
pattern that \gc{the windowed} covariances not only decay towards zero, but in fact become
negative through time, consistent with \gc{many} regions in the genome having had a
reversed fitness effect at later timepoints.

>>>>

% TODO
% - we have inconsistent notation between intro of results and figure 1 with
%   cov() 
% - address the weird barghi rep correlation point for last time

@@

Finally, we observed that in the longest study  we analyzed
\parencite{Barghi2019-qy}, some genome-wide temporal covariances become
negative at future timepoints (see the first two rows in Figure
\ref{fig:figure-1} A). This shows that alleles that were on average going up
initially are later going down in frequency, i.e. that the average direction of
selection experienced by alleles has flipped. This must reflect either a change
in the environment or the genetic background, due to changing epistatic
relationships among alleles or  recombination breaking up selective alleles.
Such reversals of selective dynamics could be occurring at other time-points
but the signal of a change in the direction of selection at particular loci may
be washed out when we calculate our genome-wide average temporal covariances.
To address this limitation, we calculated the distribution of the temporal
covariances over 100kb genomic windows (Figure \ref{fig:figure-3}, pooling
across all replicates see Supplementary Figure
\ref{suppfig:barghi-offset-replicate-panels} for individuals replicates).  The
covariance of each tile will be noisy, due to sampling and genetic drift, and
the neutral distribution of the covariance is complicated due to linkage
disequilibria (which can occur over long physical distances in E\&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}). \vb{To address
this}, we have developed a permutation-based procedure that constructs a null
distribution by randomly flipping the signs of the   allele frequency changes
per-genomic window. This destroys the systematic covariances created by linked
selection \vb{and} creates a sampling distribution of the covariances
spuriously created by neutral genetic drift while preserve the complex
dependencies between adjacent loci created by linkage disequilibrium (see
Supplementary Material Section \ref{supp:empirical-null} for more details on
this approach).  This empirical neutral null distribution is conservative in
the sense that the variances of the covariances are wider than expected under
drift alone as they include the effect of selection on the allele frequency
change within a time-interval, just not between time-intervals. We see (Figure
\ref{fig:figure-3} A and B) that windowed temporal covariances between close
timepoints are skewed positive (a heavy right tail), while between more distant
timepoints these windowed temporal covariances tend to shift to become more
negative (a heavy left tail).  We quantified the degree to which the left and
right tails are inflated compared to the null distribution as a function of
time, and see excesses in both tails in Figure \ref{fig:figure-3} C. This
finding is also robust to sign-permuting allele frequency changes on a
chromosome-level, the longest extent that gametic linkage disequilibria can
extend {\bf XXX ????} (Supplementary Figure
\ref{suppfig:barghi-tailprobs-seqid}). We see a striking pattern that the
windowed covariances not only decay towards zero, but in fact become negative
through time, consistent with many regions in the genome having had a reversed
fitness effect at later timepoints.
